Bayesian Exploration in Deep Reinforcement Learning

### 2022-08-25 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
\usepackage{minted}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\begin{minted}[mathescape,
  linenos,
  numbersep=5pt,
  gobble=2,
  frame=lines,
  framesep=2mm]{csharp}
string title = "This is a Unicode π in the sky"
/*
Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
of an $n$-sided regular polygon circumscribing a
circle of diameter $d$.
*/
const double pi = 3.1415926535
\end{minted}

>>>>

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
\usepackage{algorithm}
\usepackage{algpseudocode}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\begin{algorithm}
  \caption{An algorithm with caption}\label{alg:cap}
  \begin{algorithmic}
  \Require $n \geq 0$
  \Input
    1
  \EndInput
  \State $S \sim \N(0,I_{\lvert \A \rvert})$
  \State $z \gets v^(S; )$
  \State $N \gets n$
  \While{$N \neq 0$}
  \If{$N$ is even}
      \State $X \gets X \times X$
      \State $N \gets \frac{N}{2}$  \Comment{This is a comment}
  \ElsIf{$N$ is odd}
      \State $y \gets y \times X$
      \State $N \gets N - 1$
  \EndIf
  \EndWhile
  \end{algorithmic}
\end{algorithm}
